%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=1,top=1.25cm,bottom=0.5cm,left=1cm,right=1cm]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

% Expand the width for \phone, \email, \linkedin, \github to be on one line
\patchcmd{\makehead}% <cmd>
  {0.8\textwidth}% <search>
  {\linewidth}% <replace>
  {}{}% <success><failure>

\usepackage{ragged2e}

\nopagenumbers{}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Hien} % Your first name
\familyname{Tu} % Your last name

% All information in this block is optional, comment out any lines you don't need
% \title{Curriculum Vitae}
% \address{123 Broadway}{City, State 12345}
\mobile{(365) 888 5087}
% \phone{(000) 111 1112}
% \fax{(000) 111 1113}
\email{tun1@mcmaster.ca}
\social[linkedin]{nguyen-gia-hien-tu}
\social[github]{nguyen-gia-hien-tu}

% \homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
% \extrainfo{additional information}
% \photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
% \quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage

% \recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
\recipient{\vspace{-2.0em} HR Department}{Company Name\\Company Address\\City, State}
\vspace{-2.0em}
\date{\today} % Letter date
\opening{Dear Hiring Team,} % Opening greeting
\closing{Sincerely,} % Closing phrase
% \enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents


\makelettertitle % Print letter title

\justifying

Innovation is a crucial quality that a company requires to accelerate in the continuously developing world. In addition to my interest in innovation and in-class knowledge, I have obtained real-world experience through my co-op program. Given the mentioned reasons, I am writing to express my interest in the \textbf{12-month} position of \textbf{Data Scientist Co-op} at \textbf{AMD}, posted on the McMaster Engineering Co-op and Career Services website.

I am currently enrolled in my \textbf{final year} of the \textbf{Computer Science Co-op} program and have maintained a \textbf{CGPA} of \textbf{4/4} throughout my academic career. Throughout the courses, I have learned multiple programming languages including \textbf{Python}, \textbf{Java}, \textbf{Haskell} and received an introduction to \textbf{web development} using \textbf{HTML}, \textbf{CSS}, \textbf{JS} and \textbf{Django}. Furthermore, through several labs and assignments, I have developed my \textbf{code testing} and \textbf{debugging} skills with \textbf{Pytest} and \textbf{JUnit}. Moreover, I have enhanced my \textbf{clean-code writing} and \textbf{documentation} skills using \textbf{Pylint} and \textbf{Doxygen}.

In addition to my education, I have gained real-world experience through undertaking various responsibilities in the \textbf{16-month co-op} program with \textbf{Sanofi Global Data and AI} team as a \textbf{Software Engineer Intern}. During my co-op, I have extensively broadened my software development and design thinking skills by developing and maintaining the company's internal platform. More specifically, I developed and maintained an internal platform API using \textbf{FastAPI}, a high-performance \textbf{RESTful API framework}; \textbf{Pydantic} and \textbf{SQLModel}. Furthermore, I was able to actively learn and apply latest \textbf{cloud-native} technologies including a wide range of services in \textbf{Amazon Web Services (AWS)} such as EC2, EBS, EKS, ECR, S3, RDS, Route53; containerization platform such as \textbf{Docker} and \textbf{Kubernetes}. Moreover, I was exposed to \textbf{DevOps} practices by maintaining and improving \textbf{CI/CD pipeline} with \textbf{GitHub Actions}, \textbf{ArgoCD}, \textbf{Helm}, \textbf{Terraform} and shell scripting (\textbf{Bash}) following \textbf{GitOps} approach.

During my co-op experience, I have also gained and advanced invaluable soft skills. For instance, as part of both the customer support and development teams of a \textbf{global} company, I have enhanced my \textbf{communication} and \textbf{collaboration} and \textbf{time management} skills by replying to approximately \textbf{2000} emails from users, in a team of three customer support members, and work with other developers in different time zones, following \textbf{Agile} model. Furthermore, I have exhibited \textbf{documentation} skill by creating training guides for new users and developers, documenting new and existing features as well as updating work progress on different tasks through \textbf{Jira} tickets.

Aside from academic and work experience, I have improved and gained invaluable soft skills and technical skills by creating a logic puzzle game using \textbf{Java}. Through the process of building the project, I have developed my \textbf{self-learning} skills to learn the \textbf{Java Swing} framework to create the game user interface and learned to \textbf{apply in-class knowledge} on Java to develop the game logic. Furthermore, I have enhanced my \textbf{critical thing} and \textbf{problem solving skills} as the game not only requires programming skills but mathematical knowledge, specifically, knowledge in matrices and reduced row echelon from linear algebra, is also needed.

% Futhermore, I have also developed essential soft skills as an \textbf{undergraduate teaching assistant} at McMaster University. I have developed my \textbf{communication skills} through conducting weekly tutorials and office hours to assist the students with their knowledge in a functional programming language named Haskell. Additionally, carrying the teaching assistant job while maintaining good standings in 5 courses has further improved my \textbf{time management skills} as well as \textbf{organization skills}. These skills were further strengthened through attending weekly meetings with the professor to report current progress and discuss future work.

% In addition, as a member of the \textbf{McMaster Start Coding} club, I enhanced my teamwork and communication skills by collaborating in a group of four, including two kids and two mentors, to create a game promoting Covid-19 awareness using the club's online tool based on \textbf{Elm} at the beginning of the pandemic. As the leader of the team, I have exhibited my \textbf{leadership skills} by assigning tasks to the members where the kids would draw the figures while the other mentor and I were responsible for the mechanism of the game. During the work, I constantly checked the progress and provided support for the kids when needed.

With my skills and abilities, I am confident that I will be suitable for the position. I would appreciate the opportunity to meet and further discuss my qualifications. Please contact me at \textbf{(365) 888 5087} or at \href{mailto:tun1@mcmaster.ca}{tun1@mcmaster.ca} to arrange an interview at your earliest convenience. Thank you for your time and consideration. \\

Sincerely, \\
\textbf{Hien Tu}

% \makeletterclosing % Print letter signature

\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------


\end{document}